% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Work experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experienceWithReferenceNoTechno
  {Present}       {Tunis Engineering Manager | Scrum Master}{\href{https://www.influans.com}{Influans \faExternalLink}}{Tunis, Tunisia}
  {July 2018}      {Influans cloud platform enables any brand or retailer to deploy ultimate personalization campaigns, that target the right person with the right deal.}
    {
      \begin{itemize}
        \item Grow, develop a cross site engineering team (Tunis and Paris).
        \item Clear obstacles and remove impediments.
        \item Protect the team from outside interruptions and distractions.
        \item Help the engineering team become more autonomous and improve continuously.
        \item Animate daily delivery pace through agile processes (sprints, sprint plannings, retrospectives, grooming meetings, daily stand ups ..)
        \item Communicate with stakeholders and other teams Scrum masters and product owners about work synchronization, deadlines and evolution in delivery pace.
        \item Get team members feedback and discuss ways of improvement regularly in one to one meetings (once a sprint).
        \item annual and mid year reviews.
      \end{itemize}
    }
    {Johnny Mkhael, VP Engineering} {johnny.mkhael@gmail.com}
  \emptySeparator   
  \experienceWithReferenceNoTechno
    {June 2018}       {Team Lead}{\href{https://www.influans.com}{Influans \faExternalLink}}{Tunis, Tunisia}
    {July 2016}      {Influans cloud platform enables any brand or retailer to deploy ultimate personalization campaigns, that target the right person with the right deal.}
    {
      \begin{itemize}
        \item Grow, develop and lead Tunis engineering team.
        \item Animate daily delivery pace through agile processes (sprints, ceremonies, daily stand ups...)
        \item Design, build and maintain efficient, reusable, and reliable code.
        \item Provide day to day project execution guidance to team members.
        \item Spend ~50\% of my time as individual engineer contributor within the team.
        \item Communicate with stakeholders and other team leaders about work synchronization, deadlines and evolution in delivery pace.
      \end{itemize}
    }
    {Nicolas Peidro, R\&D manager} {nicolas.peidro@gmail.com}
  \emptySeparator   
  \experienceWithReference
    {June 2016}       {Senior Developer}{\href{https://www.influans.com}{Influans \faExternalLink}}{Tunis, Tunisia}
    {September 2015}      {Influans cloud platform enables any brand or retailer to deploy ultimate personalization campaigns, that target the right person with the right deal.}
    {
      \begin{itemize}
        \item Develop 'Campaign manager' on-boarding system (CSV, FTP, Dropbox, E-commerce connectors)
        \item Mentor junior developers in achieving sprint goals and help them produce quality code.
        \item Provide code reviews and general coding guidelines.
        \item Provide estimations for new features and study impacts on the platform.
      \end{itemize}
    }
    {Java 8, Spring framework, Maven, JUnit, Mockito, Swagger, Apache Avro, Apache Kafka, MongoDB, ElasticSearch, Git, Apache Tomcat, Jenkins CI, Nexus}
    {Nicolas Peidro, R\&D manager} {nicolas.peidro@gmail.com}
  \emptySeparator  
  \experience
    {October 2015}   {Team lead}{Pinhole}{Tunis, Tunisia}
    {March 2014} {Pinhole is a Tunisian start up specialized in catch-up TV and video on-demand applications.}
                    {
                      \begin{itemize}
                        \item Develop movies / kids / series / configuration and launcher applications for android TV Boxes.
                        \item Develop RevBox management web application for sales and stock management.
                        \item Develop RevBox remote control backend application that offers a REST API to get and search movies and series.
                        \item Develop RevBox voice control application that enables searching for content via voice commands.
                        \item Configure and manage ElasticSearch, backend and database servers.
                        \item Control deployment on test and production servers.
                        \item Push new versions remotely to all sold RevBox devices.
                      \end{itemize}
                    }
                    { Play Framework 2.3.x, Ebean, Google Guice, Jackson, ElasticSearch, EhCache, Android, Postgresql, SqLite, ElasticSearch, Heroku, Azure BLOBS, PubNub, Logentries, New Relic, Mandrill, Git}
  \emptySeparator
  \experience
    {February 2014}   {Backend developer}{Pinhole}{Tunis, Tunisia}
    {January 2013} {Pinhole is a Tunisian start up specialized in catch-up TV and video on-demand applications.}
                    {
                      \begin{itemize}
                        \item Develop application REST API.
                        \item Develop an Akka based real time chat system.
                        \item Develop and integrate an advanced web video player (it enable playing videos, display pre-roll and in-roll ads, comment a precise video moment, autoplay )
                        \item Develop Pinhole administration app.
                        \item Add features to Pinhole ads application.
                        \item Configure Elastic search server and develop search functionalities (autocomplete and advanced search)
                        \item Monitor Heroku, Amazon AWS and database servers.
                        \item manage release to production servers.
                      \end{itemize}
                    }
                    {Play Framework 2.2.x, Ebean, Google Guice, Jackson, MongoDB, ElasticSearch, EhCache, Mockito, Mustache, scribe, AngularJs, semantic-ui, TwitterBootstrap, Jquery, Postgresql, Sublime Video, Heroku, Amazon S3, Amazon EC2,Logentries, New Relic, Mandrill , Git}
  \emptySeparator
  \experience
    {December 2012}   {Oracle ADF Trainer and technical Lead}{B.G.I.}{Tunis, Tunisia}
    {September 2011} {B.G.I is a company specialized in Software solutions development. It is well known in the Tunisian hotel and banking industry circles.}
                    {
                      \begin{itemize}
                        \item Train experienced Java developers to build Oracle 11g ADF (Application Data Framework) applications.
                        \item Prepare course on how to develop, test, and deploy fully functional ADF Web applications.
                        \item Bring guidance and assist technical teams.
                      \end{itemize}
                    }
                    {Oracle ADF Fusion (ADF Faces, JSF2.0, BC4j components), Weblogic 11g, Oracle 10G}
  \emptySeparator
\end{experiences}
